Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-19 journal/article.tex
Success: Choosing the agile model

@@

>>>>

% Keep things simple

One advice given by few cases was to keep the organization simple. Beavers [P5]
describes that attempting to operate in a complex and global setting complicated
even simple agile practices. The organizational chart was simplified, which was
welcomed by both employees and managers [P5]. Rather than focusing on detail in
process, communication practices, and tools the focus should be on engaging the
teams [P40].

% Emphasize principles over mechanics

In a number of studies it was described that during transformation the
principles of agile should be emphasized over practices and simple mechanics
[P46, P48]. When people understand the agile values they will also understand
why the chage is being done and feel motivated [P1, P16, P42].
The people centric nature of agile development should be communicated correctly.
McDowell and Dourambeis [P32] describe how the organization launched a series of
communications events especially designed to emphasize the reasons behind the
agile practices.

@@

% ??
In order to draw the most out of agile teams should innovate and find on
practices that really work for their case [P40, P41]

% ??
Especially inexperienced coaches and Scrum masters made mistakes in focusing too
much on the implementation of practces [P23, P30].
